Concrete Semantics for Pushdown Analysis:\\The Essence of Summarization

### 2013-10-11 content.tex
Fixed claims of correctness w.r.t. concerns about lost paths given memoization.

@@

{
\setlength{\abovedisplayskip}{0pt}
\setlength{\belowdisplayskip}{4pt}
\setlength{\abovedisplayshortskip}{0pt}
\setlength{\belowdisplayshortskip}{8pt}
\begin{align*}
  \mastate \in \sa{State} &= (\Expr \times \Env) \times \Store \times \Kont \\
  \System &= \wp(\sa{State}) \times \wp(\sa{State}) \times \KTab \times \Memo \\
  {\mathcal F} &: \sa{\State} \to \System \to \System \\
  {\mathcal F}(\mastate_0)(S, F, \mktab, \mmemo) &= (S \cup S', F', \mktab', \mmemo') \\
  \text{where } I &= \setbuild{\mstate'}{\mastate \in F, \wn(\mastate,\mktab,\mmemo) \stepto \mstate'} \\
                \wn(\tpl{(\mexpr,\menv),\mstore,\mkont},\mktab,\mmemo)
                   &= \tpl{(\mexpr,\menv),\mstore,\mkont,\mktab,\mmemo}
\end{align*}
\begin{minipage}{.55\linewidth}
  \begin{align*}
    \mktab' &=  \bigsqcup\setbuild{\mktab'}{\wn(\_, \_, \mktab', \_) \in I} \\
    \mmemo' &= \bigsqcup\setbuild{\mmemo'}{\wn(\_, \_, \_, \mmemo') \in I}
  \end{align*}
\end{minipage}
\begin{minipage}{.40\linewidth}
  \begin{align*}
    S' &= \setbuild{\mastate'}{\wn(\mastate', \_, \_, \_) \in I} \cup \set{\mastate_0}\\
    F' &= S' \setminus S
  \end{align*}
\end{minipage}
}
%%

@@

%%
We should expect that a pushdown analysis would predict this evaluates to true, and there are no loops in the program.
%
0CFA~\citep{dvanhorn:Shivers:1991:CFA} claims there is a loop from the second call of \texttt{id} to the first, and thusly predicts this program evaluates to true or false.
%
PDCFA claims there is no loop, and depending on the implementation, that the result is true or false (paper), or just true (implemented).
\footnote{This is because the paper steps every seen state with the current store every iteration, but the implementation only steps states that need stepping.}
%
The example evaluation is in \autoref{fig:ex-eval}.
%
We maintain enough context to distinguish the return points of \texttt{id} to not rebind \texttt{y} to 1.
%
When determining control flow through the expression, we consult $\mmemo$ to continue past function calls, so there is no confusion about a back edge from the second call to \texttt{id}.
%

\begin{figure}
  \centering
    \begin{minipage}{0.55\linewidth}
      \begin{center}
        $\begin{array}{l}\includegraphics[scale=0.65]{example1}\end{array}$ \\
        $\Downarrow$ \\
        $\begin{array}{l}\includegraphics[scale=0.65]{example2}\end{array}$ \\
        $\Downarrow$ \\
        $\begin{array}{l}\includegraphics[scale=0.65]{example3}\end{array}$
      \end{center}
    \end{minipage}
    \begin{minipage}{0.43\linewidth}
      \begin{center} {\small
        \begin{tabular}{|l|c|c|}
          \hline
          \# & $\mstore$ & $\mkont$ \\
          \hline
          0 & $[{\tt id} \mapsto \set{(\slam{\mvar}{\mvar},\bot)}]$ & $\mkont_0$ \\
          1 & $\mstore_0[{\tt \mvar} \mapsto \set{0}]$ & $\krt{\mctx_0}$ \\
          2 & $\mstore_1[{\tt y} \mapsto \set{0}]$ & $\mathbf{lt}({\tt z}, {\tt (}\le\ {\tt y}\ {\tt z)})$ \\
          3 & $\mstore_2[{\tt x} \mapsto \set{0,1}]$ & $\krt{\mctx_1}$ \\
          4 & $\mstore_3[{\tt z} \mapsto \set{0,1}]$ & $\kmt$ \\
          \hline
        \end{tabular}} \\[10pt]
      {\small
        \begin{tabular}{|l|c|}
          \hline
          \# & $\mctx$ \\
          \hline
          0  & $(({\tt x}, \iota), \mstore_1)$ \\
          1  & $(({\tt x}, \iota), \mstore_3)$ \\
          \hline
        \end{tabular}}
      \\[10pt]
      {\small
        \begin{tabular}{|l|c|c|c|}
          \hline
          \# & $\mktab$ & $\mmemo$ \\
          \hline
          0  & $[\mctx_0 \mapsto \set{\mkont_0}]$ & $[\mctx_0 \mapsto \set{0}]$ \\
          1  & $\mktab_0[\mctx_1 \mapsto \set{\mkont_2}]$ & $\mmemo_0[\mctx_1 \mapsto \set{0,1}]$ \\
          \hline
        \end{tabular}}    
    \end{center}
  \end{minipage}
Where $\mkont_0 = \mathbf{lt}({\tt y}, {\tt (let\ ([z\ (id\ 1)])\ (}\le\ {\tt y}\ {\tt z))}, \iota)$
\caption{Example analysis evaluation}
\label{fig:ex-eval}
\end{figure}
% %% FIXME stores in memo-table
% \begin{enumerate}
% \item{\texttt{(id 0)} steps to \texttt{x} at $\krt{((\texttt{x}, [\texttt{x}\mapsto\texttt{x}]), \mstore_0)}$ with $\mstore_1 =
%     \mstore_0[\texttt{x} \mapsto \set{0}]$ and
%     (let $\mctx_1 = ((\texttt{x},[\texttt{x}\mapsto\texttt{x}]),\mstore_1)$,
%          $\mkont_1 = \klet{\texttt{y}, \texttt{(let ([z (id 1)]) ($\le$ y z))}, [\texttt{id}\mapsto{\texttt{id}}]}$)
%     $\mktab_1 = [\mctx_0 \mapsto \set{\mkont_0}]$}
% \item{\texttt{0} at $\krt{\mctx_1}$ steps to $0$ at $\mkont_1$ and $\mmemo_1 = [\mctx_1 \mapsto \set{0}]$}
% \item{\texttt{0} at $\mkont_1$ steps to \texttt{(let ([z (id 1)]) ($\le$ y z))} and $\mstore_2 = \mstore_1[\texttt{y} \mapsto \set{0}]$}
% \item{\texttt{(let ([z (id 1)]) ($\le$ y z))} steps to \texttt{(id 1)} at \\
%       $\klet{\texttt{z}, \texttt{($\le$ y z)}, [\texttt{id} \mapsto \texttt{id}, \texttt{y} \mapsto \texttt{y}]}$
%       (call this $\mkont_2$).}
% \item{\texttt{(id 1)} steps to $x$ with $\mstore_3 = \mstore_2[\texttt{x} \mapsto \set{0,1}]$ and
%       (let $\mctx_3 = ((\texttt{x},[\texttt{x}\mapsto\texttt{x}]),\mstore_3)$) $\mktab_3 =\mktab_1[\mctx_3 \mapsto \set{\mkont_2}]$.}
% \item{\texttt{0} or \texttt{1} at $\krt{\mctx_3}$ steps to \texttt{0} or \texttt{1} at $\mkont_2$ and $\mmemo_3 = \mmemo_1[\mctx_3 \mapsto \set{0,1}]$.}
% \item{\texttt{z} gets bound to $\set{0,1}$, and \texttt{($\le$ y z)} evaluates to true.}
% \end{enumerate}

@@

Correctness follows directly from the invariants we prove of $\mktab$ and $\mmemo$ in the tabular semantics.
%
Allocation strategies are comparable if they produce equal addresses regardless of the differences in the state representations.
%
More formally, $\alloc$ and $\alloc^*$ are comparable if this implication holds:
\begin{mathpar}
  \inferrule{\mkont \in \unroll{\mktab}{\mkont'}}
            {\alloc(\tpl{\mpoint,\mstore,\mkont}) = \alloc^*(\tpl{\mpoint,\mstore,\mkont',\mktab,\mmemo})}
\end{mathpar}

@@

We add $G$ to protect against unguarded corecursion in order for the definition to be well-defined.
%
Interpreting a function with ill-founded recursion can lead to a table such that $\krt{\mctx} \in \mktab(\mctx)$.
%
The abstractions that we impose on our data might also cause this situation, even though the concrete execution might always terminate.

%%
The different tables we have encode information about execution history that we prove is invariant (\autoref{fig:inv}).
%
The first is that the memo table only contains information about previously seen contexts; we need this to infer that there was at least one call leading to the memoized context such that we can use stack irrelevance to justify skipping to the memoized result.
%
The second, $\phi_{\reachable}$, states that all the calling contexts in the continuation table reach some unrolling of the current state.
%
The final invariant, $\phi_{\memo}$, states that the memo table is correct: all calling contexts reach the memoized result, with the calling context's continuation in the tail (to justify using stack-irrelevance).

\begin{figure}
  \centering
  \begin{align*}
    \inv(\tpl{\mpoint, \mstore, \mkont, \mktab, \mmemo}) &=
    \dom(\mmemo) \subseteq \dom(\mktab) \\
    &\wedge \forall (\mpoint',\mstore') \in \dom(\mktab), \mkont''
    \in \mktab(\mpoint',\mstore'),
    \mkont' \in \unroll{\mktab}{\mkont'', \emptyset}. \\
    &\qquad \phi_{\reachable} \wedge \phi_{\memo} \\
    \text{where } \phi_{\reachable} &= \exists \mkont'' \in
    \unroll{\mktab}{\mkont,\emptyset}.
    \tpl{\mpoint', \mstore', \mkont'} \stepto^* \tpl{\mpoint, \mstore, \mkont''} \\
    \phi_{\memo} &=
    \forall (\mval, \mstore'') \in \mmemo(\mpoint',\mstore'). \\
    &\qquad \exists \mtrace\equiv\tpl{\mpoint', \mstore', \mkont'}
    \stepto^* \tpl{\mval,\mstore'', \mkont'}.
    \hastail(\mtrace,\mkont') \\
  \end{align*}
  \caption{Table invariants}
\label{fig:inv}
\end{figure}
\begin{lemma}[Table invariants]\label{lem:tab-inv}
  If $\inv(\mstate)$ and $\mstate \stepto \mstate'$ then $\inv(\mstate')$.
\end{lemma}

@@

\begin{claim}(Correctness of PDCFA)\label{thm:pdcfa-tabular}
  Tabular semantics has a bisimulation with the standard semantics with comparable allocation strategies.
\end{claim}

Finally, we can show that even if the tables are shared amongst all states, they are precise enough to not interfere with the results.
\begin{claim}[Equivalence with global tables]\label{thm:global}
  Tabular semantics has a bisimulation with memo-and-k-table-widened semantics.
\end{claim}

@@

\begin{align*}
  \reaches(\mathit{root}, \mstore) &= \setbuild{b}{\maddr \in \mathit{root}, \maddr \rightsquigarrow_\mstore^* b} \\
   &
               \inferrule{\mval \in \mstore(\maddr) \\
                             b \in \touches(\mval)}
                            {\maddr \rightsquigarrow_\mstore b}
\end{align*}

This semantics of course enjoys the soundness properties that GC does not introduce dangling pointers (\autoref{thm:gc-pointers}), equal length traces are equal up to GC (in the concrete) (\autoref{thm:gc-concrete}), and abstractions are sound with respect to collected states (\autoref{thm:gc-sound}).
%
Technically since this semantics inspects the touched addresses of the continuation, the set of touched addresses should be considered part of the ``context'' in the $\mathbf{rt}$ continuations.
%
This extra context can be overlooked, since that means the computed touched addresses will be an overapproximation of what is already sound.
%
More touched addresses means a less effective GC, but this is an acceptable tradeoff for a possibly smaller state space.
%
\begin{claim}[No dangling pointers]\label{thm:gc-pointers}
  All addresses in $\Gamma(\mstate)$ are in the domain of $\Gamma(\mstate).\mstore$.
\end{claim}

@@

\begin{enumerate}
\item{stack allocation for some bindings in an additional $\mframe \in \Store$}
\item{strong updates on stack frames for resolved non-determinism}
\end{enumerate}
There are two orthogonal features of the semantics, embodied by our semantics' two metafunctions ($\bind$ and $\lookup$, respectively in \autoref{fig:frame-semantics}).
%
The first of these is an addition to the stack-less context.

@@

%%
The second of these is to ameliorate a problem they call ``fake rebinding.''
%
That is, since bindings in the abstract represent several values, we don't want to reference a variable \texttt{x} in two different places and have it resolve to two different values.
%
In AAM, a variable reference non-deterministically steps to all possible values associated with that variable.
%
Here we want to say that once \texttt{x} is considered to stand for value $v$, then all subsequent references of \texttt{x} should be $v$.
%
If they are not all considered $v$, it looks as if \texttt{x} was rebound; it hasn't, and thus it is a ``fake rebinding.''
%
CFA2 does not step to all values on variable reference, but instead carries all its values around in superposition until they need to be observed at, say, a function call.
%
We give a simplified semantics that is more along the AAM style, but CFA2's approach can easily be recovered from it.\footnote{Our Redex model implements the fake rebinding strategy CFA2 itself employs.}
%%

@@

\begin{claim}[Correctness of CFA2]\label{thm:cfa2}
  Tabular semantics has a bisimulation with standard semantics.
\end{claim}
This proof has the same structure as that of PDCFA.

@@

\begin{claim}\label{thm:concrete-sr}
  Tabular semantics has a bisimulation with standard semantics given fresh allocation.
\end{claim}

@@

\begin{claim}\label{thm:sound-sr}
  Tabular semantics simulates standard semantics with abstract allocation.
\end{claim}

>>>>

This semantics is only correct for fresh allocation strategies, which in turn make the reduction relation deterministic.
%
As it is, the CESK machine simulates the tabular machine, but not the other way around;
%
if we use a finite allocation strategy, then we don't explore some non-deterministic paths that lead to different results for a function call.
%
We thus explore all paths and share the k-table and memo tables between all paths.

@@

{
\setlength{\abovedisplayskip}{0pt}
\setlength{\belowdisplayskip}{4pt}
\setlength{\abovedisplayshortskip}{0pt}
\setlength{\belowdisplayshortskip}{8pt}
\begin{align*}
  \mastate \in \sa{State} &= (\Expr \times \Env) \times \Store \times \Kont \\
  \System &= \wp(\sa{State}) \times \wp(\sa{State}) \times \KTab \times \Memo \\
  {\mathcal F} &: \sa{\State} \to \System \to \System \\
  {\mathcal F}(\mastate_0)(S, \emptyset, \mktab, \mmemo) &= (S, \emptyset, \mktab, \mmemo) \\
  {\mathcal F}(\mastate_0)(S, F\cup\set{\mastate}, \mktab, \mmemo) &= (S \cup S', F\cup F', \mktab', \mmemo') \\
  \text{where } I &= \setbuild{\mstate'}{\wn(\mastate,\mktab,\mmemo) \stepto \mstate'} \\
                \wn(\tpl{(\mexpr,\menv),\mstore,\mkont},\mktab,\mmemo)
                   &= \tpl{(\mexpr,\menv),\mstore,\mkont,\mktab,\mmemo}
\end{align*}
\begin{minipage}{.55\linewidth}
  \begin{align*}
    \mktab' &=  \bigsqcup\setbuild{\mktab'}{\wn(\_, \mktab', \_) \in I} \\
    \mmemo' &= \bigsqcup\setbuild{\mmemo'}{\wn(\_, \_, \mmemo') \in I}
  \end{align*}
\end{minipage}
\begin{minipage}{.40\linewidth}
  \begin{align*}
    S' &= \setbuild{\mastate'}{\wn(\mastate', \_, \_) \in I} \cup \set{\mastate_0}\\
    F' &= S' \setminus S
  \end{align*}
\end{minipage}
}
%%

@@

%%
We should expect that a pushdown analysis would predict this evaluates to true, and there are no loops in the program.
%
0CFA~\citep{dvanhorn:Shivers:1991:CFA} claims there is a loop from the second call of \texttt{id} to the first, and thusly predicts this program evaluates to true or false.
%
PDCFA claims there is no loop, and depending on the implementation, that the result is true.
%
The example evaluation is in \autoref{fig:ex-eval}.
%
We maintain enough context to distinguish the return points of \texttt{id} to not rebind \texttt{y} to 1.
%
When determining control flow through the expression, we consult $\mktab$ to continue past function returns, so there is no confusion about a back edge from the second call to \texttt{id}.
%

\begin{figure}
  \centering
    \begin{minipage}{0.55\linewidth}
      \begin{center}
        $\begin{array}{l}\includegraphics[scale=0.5]{example1}\end{array}$ \\
        $\Downarrow$ \\
        $\begin{array}{l}\includegraphics[scale=0.5]{example2}\end{array}$ \\
        $\Downarrow$ \\
        $\begin{array}{l}\includegraphics[scale=0.5]{example3}\end{array}$
      \end{center}
    \end{minipage}
    \begin{minipage}{0.43\linewidth}
      \begin{center} {\small
        \begin{tabular}{|l|c|c|}
          \hline
          \# & $\mstore$ & $\mkont$ \\
          \hline
          0 & $[{\tt id} \mapsto \set{(\slam{\mvar}{\mvar},\iota)}]$ & $\mkont_0$ \\
          1 & $\mstore_0[{\tt \mvar} \mapsto \set{0}]$ & $\krt{\mctx_0}$ \\
          2 & $\mstore_1[{\tt y} \mapsto \set{0}]$ & $\mathbf{lt}({\tt z}, {\tt (}\le\ {\tt y}\ {\tt z)}, \iota)$ \\
          3 & $\mstore_2[{\tt x} \mapsto \set{0,1}]$ & $\krt{\mctx_1}$ \\
          4 & $\mstore_3[{\tt z} \mapsto \set{0,1}]$ & $\kmt$ \\
          \hline
        \end{tabular}} \\[10pt]
      {\small
        \begin{tabular}{|l|c|}
          \hline
          \# & $\mctx$ \\
          \hline
          0  & $(({\tt x}, \iota), \mstore_1)$ \\
          1  & $(({\tt x}, \iota), \mstore_3)$ \\
          \hline
        \end{tabular}}
      \\[10pt]
      {\small
        \begin{tabular}{|l|c|c|c|}
          \hline
          \# & $\mktab$ & $\mmemo$ \\
          \hline
          0  & $[\mctx_0 \mapsto \set{\mkont_0}]$ & $[\mctx_0 \mapsto \set{0}]$ \\
          1  & $\mktab_0[\mctx_1 \mapsto \set{\mkont_2}]$ & $\mmemo_0[\mctx_1 \mapsto \set{0,1}]$ \\
          \hline
        \end{tabular}}    
    \end{center}
  \end{minipage}
Where $\mkont_0 = \mathbf{lt}({\tt y}, {\tt (let\ ([z\ (id\ 1)])\ (}\le\ {\tt y}\ {\tt z))}, \iota)$
\caption{Example analysis evaluation}
\label{fig:ex-eval}
\end{figure}
% %% FIXME stores in memo-table
% \begin{enumerate}
% \item{\texttt{(id 0)} steps to \texttt{x} at $\krt{((\texttt{x}, [\texttt{x}\mapsto\texttt{x}]), \mstore_0)}$ with $\mstore_1 =
%     \mstore_0[\texttt{x} \mapsto \set{0}]$ and
%     (let $\mctx_1 = ((\texttt{x},[\texttt{x}\mapsto\texttt{x}]),\mstore_1)$,
%          $\mkont_1 = \klet{\texttt{y}, \texttt{(let ([z (id 1)]) ($\le$ y z))}, [\texttt{id}\mapsto{\texttt{id}}]}$)
%     $\mktab_1 = [\mctx_0 \mapsto \set{\mkont_0}]$}
% \item{\texttt{0} at $\krt{\mctx_1}$ steps to $0$ at $\mkont_1$ and $\mmemo_1 = [\mctx_1 \mapsto \set{0}]$}
% \item{\texttt{0} at $\mkont_1$ steps to \texttt{(let ([z (id 1)]) ($\le$ y z))} and $\mstore_2 = \mstore_1[\texttt{y} \mapsto \set{0}]$}
% \item{\texttt{(let ([z (id 1)]) ($\le$ y z))} steps to \texttt{(id 1)} at \\
%       $\klet{\texttt{z}, \texttt{($\le$ y z)}, [\texttt{id} \mapsto \texttt{id}, \texttt{y} \mapsto \texttt{y}]}$
%       (call this $\mkont_2$).}
% \item{\texttt{(id 1)} steps to $x$ with $\mstore_3 = \mstore_2[\texttt{x} \mapsto \set{0,1}]$ and
%       (let $\mctx_3 = ((\texttt{x},[\texttt{x}\mapsto\texttt{x}]),\mstore_3)$) $\mktab_3 =\mktab_1[\mctx_3 \mapsto \set{\mkont_2}]$.}
% \item{\texttt{0} or \texttt{1} at $\krt{\mctx_3}$ steps to \texttt{0} or \texttt{1} at $\mkont_2$ and $\mmemo_3 = \mmemo_1[\mctx_3 \mapsto \set{0,1}]$.}
% \item{\texttt{z} gets bound to $\set{0,1}$, and \texttt{($\le$ y z)} evaluates to true.}
% \end{enumerate}

@@

Correctness follows directly from the invariants we prove of $\mktab$ and $\mmemo$ in the tabular semantics.
%
Allocation strategies are comparable if they produce equal addresses regardless of the differences in the state representations.
%
More formally, $\alloc$ and $\alloc^*$ are comparable if this implication holds:
\begin{mathpar}
  \inferrule{\mkont \in \unroll{\mktab}{\mkont', \emptyset}}
            {\alloc(\tpl{\mpoint,\mstore,\mkont}) = \alloc^*(\tpl{\mpoint,\mstore,\mkont',\mktab,\mmemo})}
\end{mathpar}

@@

We add $G$ to protect against unguarded corecursion in order for $\mathit{unroll}$ to be well-defined.
%
Interpreting a function with ill-founded recursion can lead to a table such that $\krt{\mctx} \in \mktab(\mctx)$.
%
The abstractions that we impose on our data might also cause this situation, even though the concrete execution might always terminate.

%%
The different tables we have encode information about execution history that we prove is invariant (\autoref{fig:inv}).
%
The first is that the memo table only contains information about previously seen contexts; we need this to infer that there was at least one call leading to the memoized context such that we can use stack irrelevance to justify skipping to the memoized result.
%
The second, $\phi_{\reachable}$, states that all the calling contexts in the continuation table reach some unrolling of the current state.
%
The final invariant, $\phi_{\memo}$, states that all paths starting at a function call either reach the memoized result, or if the path does not include a return, there is an extension that will.
%
The portion of these paths between call and return hal the calling context's continuation in the tail to justify using stack-irrelevance.

\begin{figure}
  \centering
  \begin{align*}
    \inv(\tpl{\mpoint, \mstore, \mkont, \mktab, \mmemo}) &=
    \dom(\mmemo) \subseteq \dom(\mktab) \\
    &\wedge \forall (\mpoint',\mstore') \in \dom(\mktab), \mkont''
    \in \mktab(\mpoint',\mstore'),
    \mkont' \in \unroll{\mktab}{\mkont'', \emptyset}. \\
    &\qquad \phi_{\reachable} \wedge \phi_{\memo} \\
    \text{where } \phi_{\reachable} &= \exists \mkont'' \in
    \unroll{\mktab}{\mkont,\emptyset}.
    \tpl{\mpoint', \mstore', \mkont'} \stepto^* \tpl{\mpoint, \mstore, \mkont''} \\
    \phi_{\memo} &=
    \forall (\mval, \mstore'') \in \mmemo(\mpoint',\mstore'). \\
    &\qquad\exists \mtrace\equiv\tpl{\mpoint', \mstore', \mkont'} \stepto^* \tpl{\mval,\mstore'',\mkont'}. \hastail(\mtrace,\mkont')
  \end{align*}
  \caption{Table invariants}
\label{fig:inv}
\end{figure}
\begin{lemma}[Table invariants in CESK$\mathit{\Xi{}M}$]\label{lem:tab-inv}
  If $\inv(\mstate)$ and $\mstate \stepto \mstate'$ then $\inv(\mstate')$.
\end{lemma}

@@

\begin{claim}(Correctness of Concrete Summarization)\label{thm:concrete-tabular}
  The standard semantics has a bisimulation with the tabular semantics given comparable fresh allocation strategies.
\end{claim}

Finally, we can show that the reductions we find between states paired with the shared tables define a sound and complete abstraction of the CESK machine with a comparable allocation strategy.
\begin{claim}[Correctness of PDCFA]\label{thm:global}
  Widened tabular semantics reifies a relation that has a bisimulation with the standard semantics.
\end{claim}

@@

\begin{align*}
  \reaches(\mathit{root}, \mstore) = \setbuild{b}{\maddr \in \mathit{root}, \maddr \rightsquigarrow_\mstore^* b}
   \qquad
               \inferrule{\mval \in \mstore(\maddr) \\
                             b \in \touches(\mval)}
                            {\maddr \rightsquigarrow_\mstore b}
\end{align*}

This semantics of course enjoys the soundness properties that GC does not introduce dangling pointers, equal length traces are equal up to GC (in the concrete), and abstractions are sound with respect to collected states.
%
Technically since this semantics inspects the touched addresses of the continuation, the set of touched addresses should be considered part of the ``context'' in the $\mathbf{rt}$ continuations.
%
This extra context can be overlooked, since that means the computed touched addresses will be an overapproximation of what is already sound.
%
More touched addresses means a less effective GC, but this is an acceptable tradeoff for a possibly smaller state space.
%
\begin{claim}[No dangling pointers]\label{thm:gc-pointers}
  All addresses in $\Gamma(\mstate)$ are in the domain of $\Gamma(\mstate).\mstore$.
\end{claim}

@@

\begin{enumerate}
\item{stack allocation for some bindings in an additional $\mframe \in \Store$}
\item{strong updates on stack frames for resolved addresses}
\end{enumerate}
There are two orthogonal features of the semantics, embodied by our semantics' two metafunctions ($\bind$ and $\lookup$, respectively in \autoref{fig:frame-semantics}).
%
The first of these is an addition to the stack-less context.

@@

%%
The second of these is to ameliorate a problem they call ``fake rebinding.''
%
That is, since bindings in the abstract represent several values, we don't want to reference a variable \texttt{x} in two different places and have it resolve to two different values.
%
In AAM, a variable reference non-deterministically steps to all possible values associated with that variable, because there are several possible values in the store for allocated bindings.
%
Here we want to say that once \texttt{x} is considered to stand for value $v$, then all subsequent references of \texttt{x} should be $v$.
%
If they are not all considered $v$, it looks as if \texttt{x} was rebound; it hasn't, and thus it is a ``fake rebinding.''
%
CFA2 does not step to all values on variable reference, but instead carries all its values around in superposition until they need to be observed at, say, a function call.
%
We give a simplified semantics that is more along the AAM style, but CFA2's approach can easily be recovered from it.\footnote{Our Redex model implements the fake rebinding strategy CFA2 itself employs.}
%%

@@

\begin{claim}[Correctness of CFA2]\label{thm:cfa2}
  The widened tabular semantics reifies a relation that has a bisimulation with standard semantics.
\end{claim}
This proof has the same structure as that of PDCFA.

@@

\begin{claim}\label{thm:concrete-sr}
  Tabular semantics simulates the standard semantics given fresh allocation.
\end{claim}

@@

\begin{claim}\label{thm:sound-sr}
  Widened tabular semantics reifies a relation that simulates standard semantics.
\end{claim}
